An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-07-06 gas-adsorption/rsc-gas-ads-complete.tex
fix a davidsays

\begin{equation}
   \gst(\rho, T) \equiv
   %\frac{G_{\text{ads}}(\rho, T) - G_{\text{gas}}(\rho, T)}{N}\\
    \mu_{\text{ads}}(\rho, T) - \mu_{\text{gas}}(\rho, T).
  % \gst(\rho, T) &\equiv g_{\text{gas}}(\rho, T) - g_{\text{ads}}(\rho, T)
  \label{eq:g_st}
\end{equation}
The isosteric Gibbs free energy difference $\gst$ is the difference in molar
Gibbs free energy (equivalent to chemical potential) between the adsorbed gas system and
the bulk gas \emph{with the same density of gas molecules} and at the same temperature. The quantity $\gst$
does \emph{not} correspond to a change in the molar Gibbs free energy as a
molecule is adsorbed, which is zero under conditions of coexistence. The
quantity $\gst$ in a real substrate is a direct analog to $\V$ in our ideal
substrate because it is the chemical potential shift needed to impose on the
bulk gas in coexistence with the real substrate to achieve the same density as
in the substrate (compare with eqn.~\ref{eq:xi_vs_xi0}).
Figure~\ref{fig:delta-G-cartoon} illustrates $\gst$.
% David:  no longer illustrates the expt.
A hypothetical experiment to measure $\gst$ is via a piston with a removable partition that separates a volume of free space from the same volume of substrate.
Initialize the experiment with all gas in the free space and an empty substrate.
Then, slowly (i) remove the partition and (ii) use the piston to push the gas into the substrate and eliminate the free space volume, in an isothermal process.
$\gst$ is the ... \corysays{wut? energy it takes to do this or?}
%
\davidsays{Okay, here is an improved experiment to measure $\gst$.  Two containers of
equal volume are connected by a hose (with neglible volume).  One container holds
the substrate, and the other is empty (apart from gas).    The altitude of one container
is adjusted until the number of gas molecules is equal in each container.  The value
of $\gst$ is the gravitational potential energy difference of gas molecules in the two
boxes.}
% David: what is GST
Note that $\gst$ is a property
of both the substrate and the identity of the gas. Because real substrates
offer a \emph{non}-spatially uniform potential, $\gst(\rho, T)$ is a function
of $\rho$ and $T$, unlike our ideal, homogenous substrate where $\gst(\rho,
T)=\V$. Consequently, throughout this article, we show $\gst(\rho, T)$ for real
substrates at both conditions relevant to gas storage and delivery, $\pfull$
and $\pempty$.

>>>>

\begin{equation}
   \gst(\rho, T) \equiv
   %\frac{G_{\text{ads}}(\rho, T) - G_{\text{gas}}(\rho, T)}{N}\\
    \mu_{\text{ads}}(\rho, T) - \mu_{\text{gas}}(\rho, T).
  % \gst(\rho, T) &\equiv g_{\text{gas}}(\rho, T) - g_{\text{ads}}(\rho, T)
  \label{eq:g_st}
\end{equation}
The isosteric Gibbs free energy difference $\gst$ is the difference in molar
Gibbs free energy (equivalent to chemical potential) between the adsorbed gas system and
the bulk gas \emph{with the same density of gas molecules} and at the same temperature. The quantity $\gst$
does \emph{not} correspond to a change in the molar Gibbs free energy as a
molecule is adsorbed, which is zero under conditions of coexistence. The
quantity $\gst$ in a real substrate is a direct analog to $\V$ in our ideal
substrate because it is the chemical potential shift needed to impose on the
bulk gas in coexistence with the real substrate to achieve the same density as
in the substrate (compare with eqn.~\ref{eq:xi_vs_xi0}).
% Figure~\ref{fig:delta-G-cartoon} illustrates  $\gst$.
% David:  no longer illustrates the expt.
% A hypothetical experiment to measure $\gst$ is via a piston with a removable partition that separates a volume of free space from the same volume of substrate.
% Initialize the experiment with all gas in the free space and an empty substrate.
% Then, slowly (i) remove the partition and (ii) use the piston to push the gas into the substrate and eliminate the free space volume, in an isothermal process.
% $\gst$ is the ... \corysays{wut? energy it takes to do this or?}
%
% \davidsays{Okay, here is an improved experiment to measure $\gst$.  Two containers of
% equal volume are connected by a hose (with neglible volume).  One container holds
% the substrate, and the other is empty (apart from gas).    The altitude of one container
% is adjusted until the number of gas molecules is equal in each container.  The value
% of $\gst$ is the gravitational potential energy difference of gas molecules in the two
% boxes.}
%
Figure~\ref{fig:delta-G-cartoon} illustrates a hypothetical experiment to
measure $\gst$.  Two containers of equal volume are connected by a hose.  One
container holds the substrate, and the other is empty (apart from gas).    The
altitude of one container is adjusted until the number of gas molecules is equal
in each container.  The value of $\gst$ is the gravitational potential energy
difference of gas molecules in the two boxes.

% David: what is GST
Note that $\gst$ is a property
of both the substrate and the identity of the gas. Because real substrates
offer a \emph{non}-spatially uniform potential, $\gst(\rho, T)$ is a function
of $\rho$ and $T$, unlike our ideal, homogenous substrate where $\gst(\rho,
T)=\V$. Consequently, throughout this article, we show $\gst(\rho, T)$ for real
substrates at both conditions relevant to gas storage and delivery, $\pfull$
and $\pempty$.
